---
title: "Craps Simulation"
format: html
author: Nathan Ma
---

`The avaliable wrok progress are store in craps-code.qmd and pseudocode.qmd`

## Question 1: Which probability do you want to estimate?
  - Answer: I aim to estimate the winning probability with point greater than 9 in a game of craps.


```{r, echo=FALSE}
# Load Required Functions
source("simulation.R")
set.seed(114514)
estimate_winning_probability_greater_than_9 <- function(N_trials) {
  # Input: N_trials: Vector of integers for different numbers of simulations
  # Output: Data frame summarizing winning probabilities for games with point > 9 and variability
  
  results_summary <- data.frame(
    simulations = integer(),
    win_prob_gt_9 = numeric(),
    variability = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (N in N_trials) {
    set.seed(114514)
    simulations <- run_craps_simulation(N)
    
    # Filter games where the point > 9
    games_gt_9 <- simulations[!is.na(simulations$point) & simulations$point > 9, ]
    
    if (nrow(games_gt_9) > 0) {
      # Calculate Winning Probability and Variability for Point > 9
      win_prob_gt_9 <- mean(games_gt_9$final_outcome == "win")
      variability <- sd(games_gt_9$final_outcome == "win")
    } else {
      # Handle case where no games with point > 9 occur
      win_prob_gt_9 <- NA
      variability <- NA
    }
    
    results_summary <- rbind(results_summary, data.frame(
      simulations = N,
      win_prob_gt_9 = win_prob_gt_9,
      variability = variability
    ))
  }
  
  return(results_summary)
}


# Different simulation sizes
N_trials <- c(100, 500, 1000, 5000, 10000)
simulation_results <- estimate_winning_probability_greater_than_9(N_trials)
```

## Question 2: What is the simulation result (in numbers and visuals)?
  - Answer: 

```{r}
# Print the Simulation Results
cat("Simulation Results for Point > 9:\n")
print(simulation_results)

# Visualize Winning Probability for Point > 9
library(ggplot2)

# Plot Variability vs Number of Simulations for Point > 9
ggplot(simulation_results, aes(x = simulations, y = variability)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(
    title = "Variability vs Number of Simulations (Point > 9)",
    x = "Number of Simulations",
    y = "Variability"
  ) +
  theme_minimal()

# Plot Winning Probability Convergence for Point > 9
ggplot(simulation_results, aes(x = simulations, y = win_prob_gt_9)) +
  geom_line(color = "green") +
  geom_point(color = "orange") +
  geom_hline(yintercept = mean(simulation_results$win_prob_gt_9, na.rm = TRUE), linetype = "dashed", color = "black") +
  labs(
    title = "Winning Probability vs Number of Simulations (Point > 9)",
    x = "Number of Simulations",
    y = "Winning Probability (Point > 9)"
  ) +
  theme_minimal()
```

## Interpret Results
1. The winning probability for games with point > 9 stabilizes as the number of simulations increases.
2. Variability decreases with increasing simulations, better estimates for larger simulation sizes.

