---
title: "Craps Simulation"
format: html
author: Nathan Ma
---

`The avaliable wrok progress are store in craps-code.qmd and pseudocode.qmd`

## Question 1: Which probability do you want to estimate?
  - Answer: I aim to estimate the winning probability in a game of craps.


```{r, echo=FALSE}
# Load Required Functions
source("simulation.R")
set.seed(114514)
estimate_winning_probability <- function(N_trials) {
  # Input:
  # N_trials: Vector of integers for different numbers of simulations
  #
  # Output:
  # Data frame summarizing winning probabilities and variability
  
  results_summary <- data.frame(
    simulations = integer(),
    win_prob = numeric(),
    variability = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (N in N_trials) {
    set.seed(114514)
    simulations <- run_craps_simulation(N)
    
    # Calculate Winning Probability and Variability
    win_prob <- mean(simulations$final_outcome == "win")
    variability <- sd(simulations$final_outcome == "win")
    
    results_summary <- rbind(results_summary, data.frame(
      simulations = N,
      win_prob = win_prob,
      variability = variability
    ))
  }
  
  return(results_summary)
}

# Different simulation sizes
N_trials <- c(100, 500, 1000, 5000, 10000)
simulation_results <- estimate_winning_probability(N_trials)
```

## Question 2: What is the simulation result (in numbers and visuals)?
  - Answer:

```{r}
# Print the Simulation Results
cat("Simulation Results:\n")
print(simulation_results)
library(ggplot2)

# Plot Variability vs Number of Simulations
ggplot(simulation_results, aes(x = simulations, y = variability)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(
    title = "Variability vs Number of Simulations",
    x = "Number of Simulations",
    y = "Variability"
  ) +
  theme_minimal()

# Plot Winning Probability Convergence
ggplot(simulation_results, aes(x = simulations, y = win_prob)) +
  geom_line(color = "green") +
  geom_point(color = "orange") +
  geom_hline(yintercept = mean(simulation_results$win_prob), linetype = "dashed", color = "black") +
  labs(
    title = "Winning Probability vs Number of Simulations",
    x = "Number of Simulations",
    y = "Winning Probability"
  ) +
  theme_minimal()
```

## Interpret Results
1. The winning probability stabilizes as the number of simulations increases.
2. Variability decreases with increasing simulations, showing more reliable estimates for larger simulation sizes.
3. Use this result to determine the number of simulations needed for accurate estimates in similar problems.

